A systematic search for transiting planets using \KT

### 2015-02-12 ms.tex
more intro edits

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{ketu}}

@@

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
model for the measured flux, with pointing measurements as the inputs, and
then ``de-trend'' using the mean prediction from that model.
Other data-driven approaches have been developed and applied to the \Kepler\
data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
generalized to be applicable to \KT.

@@

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
Simultaneous fitting enables a search for---and measurement of---exoplanet signals
to deliver results that are
independent of any implied estimate of the systematics, provided that the true
systematics lie in the domain of the systematics model.
DFM I WOULD SAY HERE \emph{WHY} SIMULTANEOUS FITTING LEADS TO INDEPENDENCE, AND WHAT DO YOU MEAN BY THAT?
The likelihood of the simultaneous fit of the systematics and transit signals
to the data can then be compared to the likelihood of the fit of the systematics
alone, reducing exoplanet ``search'' to a simple model comparison problem.

DFM:  HERE IS WHERE I WOULD TALK ABOUT MARGINALIZATION...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
right, because the mean and variance of the Gaussian likelihood are
analytic (though maybe expensive).)  If we \emph{do} marginalize (or
maybe either way), we need to emphasize here the difference between
simultaneously \emph{estimating} the signal and the noise as opposed
to simultaneously \emph{fitting} the signal and the noise and
marginalization out of the latter.  Key idea: Don't come to a
conclusion about (estimate) anything you don't care about, if you can
possibly avoid it!

In this \paper\ we present a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.
We assume the trends in the observed light curves in each star due to
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of
these basis vectors and a transit model.
Such a technique builds on the ideas of previous PCA-based \kepler\ planet
searches, such as those of (cite-Petigura).

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission \citep{Ricker:2014}.
\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

Catalogs of transiting planets found in the \KT\ data will be important to better
understand the physical properties, formation, and evolution of planetary systems.
These planets, especially when they orbit especially bright or late-type stars,
will be useful targets for ground-based and space-based follow-up, both for
current facilities and those planned in the near-future such as JWST.
They will also deliver input data for next-generation population inferences (cite DFM),
which in turn constrain population synthesis models.

@@

In the period search step, we use the lookup table generated by the linear
search to compute the likelihood from \eq{indtran} on a three dimensional
grid in period \period, reference time \phase, and duration \duration.
At each point, we compute the likelihood of a model where the transit depth
varies between transits and the ``correct'' simpler model where the transit
depth is constant.
The variable depth likelihood is simply the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
\end{eqnarray}
and the constant depth model is
\begin{eqnarray}
p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth is
\begin{eqnarray}\eqlabel{periodic-depth}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and the uncertainty on this depth is given by
\begin{eqnarray}\eqlabel{periodic-depth-uncert}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}

>>>>

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\jwst}{\project{JWST}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{ketu}}

@@

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
model for the measured flux, with pointing measurements as the inputs, and
then ``de-trend'' using the mean prediction from that model.
Other data-driven approaches have been developed and applied to the \kepler\
data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
generalized to be applicable to \KT.

@@

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
This method can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, this allows us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}

In this \paper\ we present a data-analysis technique for exoplanet search and
characterization that is insensitive to spacecraft-induced trends in the light
curves.
We assume that the trends in the observed light curves in each star due to
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of a
huge number of these basis vectors and a transit model.
Our method builds on the ideas of previous data-driven de-trending procedures
like Pre-search data conditioning \citep[PDC;][]{pdc1, pdc2} but we can use a
much more flexible systematics model without worrying about over-fitting.

The methods developed within this paper are highly relevant to both \KT\ and
the upcoming \tess\ mission \citep{Ricker:2014}.
\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite), similar
to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

Catalogs of transiting planets found in the \KT\ data will be important to
better understand the physical properties, formation, and evolution of
planetary systems.
These planets, especially when they orbit especially bright or late-type
stars, will be useful targets for ground-based and space-based follow-up, both
for current facilities and those planned in the near-future such as \jwst.
They will also deliver input data for next-generation population inferences
\citep{dfm}, especially for the population of planets around cool stars
\citep[for example][]{dressing}.

@@

In the period search step, we use the lookup table generated by the linear
search to compute the likelihood from \eq{indtran} on a three dimensional
grid in period \period, reference time \phase, and duration \duration.
At each point, we compute the likelihood of a model where the transit depth
varies between transits and the ``correct'' simpler model where the transit
depth is constant.
The variable depth likelihood is simply the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
\end{eqnarray}
and the constant depth model is
\begin{eqnarray}
p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth is
\begin{eqnarray}\eqlabel{periodic-depth}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and the uncertainty on this depth is given by
\begin{eqnarray}\eqlabel{periodic-depth-uncert}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}
Note that this result is \emph{marginalized} over the parameters of the
systematics model.
Therefore, this estimate of the uncertainty on the depth takes any
uncertainty that we have about the systematics into account.
